Algorithm explanation

### 2013-08-26 article/thesis.tex
Reference name prefix removal

One of the most common methods of such abstraction is predicate
abstraction\cite{DBLP:conf/cav/GrafS97} within CounterExample-Guided
Abstraction Refinement (CEGAR) framework
\cite{DBLP:conf/cav/ClarkeGJLV00,DBLP:conf/popl/BallR02,DBLP:conf/popl/HenzingerJMS02}.
An automated theorem prover finds appropriate predicates for every
program location.  An execution states at those locations is then
expressed by a Boolean valuation of the given predicates.  If the
abstraction is too coarse and a model checker discovers an infeasible
error execution path in an abstract system, the prover computes an
additional predicate at those program locations to refine the
abstraction predicates.

In order to obtain an additional abstraction predicate at program
locations along the infeasible counterexample, one class of automated
theorem provers, called an interpolating theorem prover
\cite{DBLP:journals/tcs/McMillan05,DBLP:conf/vmcai/RybalchenkoS07},
computes a separating predicate called an interpolant between two sets
of constraints; the one consists of the constraints from the program
entry point to the location, and the other consists of the constraints
from the location to the program failure.  Those constraints include
variable assignments and assertions to be satisfied originated from
conditional branches.

@@

However, by the existing interpolating theorem prover, we may not be
able to obtain a simple solution.  Consider the example below.
\begin{align*}
\varphi_1 : (x = 0 \wedge y = 0) \vee (x = 1 \wedge y = 1) \\
\varphi_2 : (x \neq 0 \wedge y = 0) \vee (x \neq 1 \wedge y = 1)
\end{align*}
Although one may be able to obtain $x = y$ as the simplest
interpolation between $\varphi_1$ and $\varphi_2$,
CSIsat\cite{DBLP:conf/cav/BeyerZM08} returns
\[ TODO \]
as a solution.

@@

\paragraph{Craig Interpolation}
Given two logical formulas $A$ and $B$ that are inconsistent each
other, we call a new preposition $I$ a \emph{Craig interpolant}
\cite{DBLP:journals/jsyml/Craig57} between $A$ and $B$ such that $I$
is implied by $A$ and inconsistent with $B$.  $I$'s vocabulary must be
only free variables that appears in both $A$ and $B$.  If $A \wedge B$
is unsatisfiable, an interpolant $I$ always exists.

@@

We incorporated our algorithm to the software model checker for
higher-order programs (MoCHi) \cite{DBLP:conf/pldi/KobayashiSU11}.  It
is specifically designed to verify the correctness of higher-orde
programs written in a small subset of ML.  It infers dependent types
for input higher-order programs \cite{DBLP:conf/ppdp/UnnoK09}.

Our implementation make use of Z3 \cite{DBLP:conf/tacas/MouraB08} as
an SMT solver.

For simplicity of the implementation, we assume that the linear
inequalities in the integer space.  Because of this, our algorithm
lost the completeness.  By using Motzkin's transpose theorem
\cite{DBLP:journals/networks/Rajan90}, it is possible to handle linear
inequalities in both $\mathbf{ax} + b \leq 0$ and $\mathbf{ax} + b <
0$.

@@

\begin{itemize}
\item CSIsat \cite{DBLP:conf/cav/BeyerZM08}
\item FOCI \cite{website:foci}
\item CLP-Prover \cite{website:clp}
\end{itemize}

@@

\paragraph{Non-linear extension}
\cite{DBLP:conf/cav/DaiXZ13}

>>>>

One of the most common methods of such abstraction is predicate
abstraction\cite{conf/cav/GrafS97} within CounterExample-Guided
Abstraction Refinement (CEGAR) framework
\cite{conf/cav/ClarkeGJLV00,conf/popl/BallR02,conf/popl/HenzingerJMS02}.
An automated theorem prover finds appropriate predicates for every
program location.  An execution states at those locations is then
expressed by a Boolean valuation of the given predicates.  If the
abstraction is too coarse and a model checker discovers an infeasible
error execution path in an abstract system, the prover computes an
additional predicate at those program locations to refine the
abstraction predicates.

In order to obtain an additional abstraction predicate at program
locations along the infeasible counterexample, one class of automated
theorem provers, called an interpolating theorem prover
\cite{journals/tcs/McMillan05,conf/vmcai/RybalchenkoS07},
computes a separating predicate called an interpolant between two sets
of constraints; the one consists of the constraints from the program
entry point to the location, and the other consists of the constraints
from the location to the program failure.  Those constraints include
variable assignments and assertions to be satisfied originated from
conditional branches.

@@

However, by the existing interpolating theorem prover, we may not be
able to obtain a simple solution.  Consider the example below.
\begin{align*}
\varphi_1 : (x = 0 \wedge y = 0) \vee (x = 1 \wedge y = 1) \\
\varphi_2 : (x \neq 0 \wedge y = 0) \vee (x \neq 1 \wedge y = 1)
\end{align*}
Although one may be able to obtain $x = y$ as the simplest
interpolation between $\varphi_1$ and $\varphi_2$,
CSIsat\cite{conf/cav/BeyerZM08} returns
\[ TODO \]
as a solution.

@@

\paragraph{Craig Interpolation}
Given two logical formulas $A$ and $B$ that are inconsistent each
other, we call a new preposition $I$ a \emph{Craig interpolant}
\cite{journals/jsyml/Craig57} between $A$ and $B$ such that $I$
is implied by $A$ and inconsistent with $B$.  $I$'s vocabulary must be
only free variables that appears in both $A$ and $B$.  If $A \wedge B$
is unsatisfiable, an interpolant $I$ always exists.

@@

We incorporated our algorithm to the software model checker for
higher-order programs (MoCHi) \cite{conf/pldi/KobayashiSU11}.  It
is specifically designed to verify the correctness of higher-orde
programs written in a small subset of ML.  It infers dependent types
for input higher-order programs \cite{conf/ppdp/UnnoK09}.

Our implementation make use of Z3 \cite{conf/tacas/MouraB08} as
an SMT solver.

For simplicity of the implementation, we assume that the linear
inequalities in the integer space.  Because of this, our algorithm
lost the completeness.  By using Motzkin's transpose theorem
\cite{journals/networks/Rajan90}, it is possible to handle linear
inequalities in both $\mathbf{ax} + b \leq 0$ and $\mathbf{ax} + b <
0$.

@@

\begin{itemize}
\item CSIsat \cite{conf/cav/BeyerZM08}
\item FOCI \cite{website/foci}
\item CLP-Prover \cite{website/clp}
\end{itemize}

@@

\paragraph{Non-linear extension}
\cite{conf/cav/DaiXZ13}
